\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\providecommand{\abs}[1]{\left\vert#1\right\vert}
\title{Assignment}
\date{\today}
\begin{document}
\maketitle
\section*{ CBSE 2019 Mathematics  Questions: 56.5.3 }
\begin{enumerate}
\item Find the  order of the differential equation of the family of circle of radius $3$ units.
\item Find the angle between the lines $\overrightarrow{r}=\brak{2\hat{i}-\hat{j}+3\hat{k}}+\lambda\brak{3\hat{i}-\hat{j}+2\hat{k}}$ and the plane. $\overrightarrow{r}.\brak{\hat{i}+\hat{j}+\hat{k}}=3$.
\item Find the co-ordinate of the point, where the line $ \dfrac{x+2}{1}=\dfrac{y-5}{3}=\dfrac{z+1}{5} $ cut the yz-plane.
\item If A=$\myvec{8&2\\3&2}$,then find $\abs{adj.A}$.
\item If $y=2\sqrt{\sec\brak{e^{2x}}}$, than find $\dfrac{dy}{dx}$.
\item Four card are drawn one by one with replacement from a well-shuffled deck of playing card. Find the probability that at least three cards are of diamonds.
\item The probability of two students $A$ and $B$ coming to school on time are $\dfrac{2}{7}$and $\dfrac{4}{7}$ respectively. assuming that the event $A$ coming on the time and $B$ coming on time are independent, Find the probability of only one of them coming to school on time.
\item Using vectors, prove that the points  $\brak{2,-1,3},\brak{3,-5,1}$and $\brak{-1,11,9}$ are co-linear.
\item For any two vectors $\overrightarrow{a}$ and $ \overrightarrow{b}$,prove that $\brak{\overrightarrow{a}x\overrightarrow{b}}^2=\overrightarrow{a}^2\overrightarrow{b}^2-\brak{\overrightarrow{a}.\overrightarrow{b}}^2$.
\item Find \begin{align*}
 \int \frac{x-1}{\brak{x-2}\brak{x-3}}dx.\end{align*}\\
\item Integrate:
\begin{align*}
\frac{e^x}{\sqrt{5-4e^x-e^{2x}}}
\end{align*}.
\item If $P\brak{A}=0.6,P\brak{B}=0.5$ and $P\brak{B|A}=0.4$, Find $P\brak{A\bigcup B}$ and $P\brak{A|B}$.
\item Find the value of $\brak{x-y}$ from the matrix equation $2\myvec{x&5\\7&y-3}+\myvec{-3&-4\\1&2}=\myvec{7&6\\15&14}.$
\item Find
\begin{align}
\int e^x\brak{\cos x-\sin x}\csc^2 x dx.
\end{align}
\item Find the differential equation of the family of curves represented by $y^2=a\brak{b^2-x^2}$.
\item Let an operation *on the set of natural number N be defined by $a*b=a^b$.Find $\brak{i}$ where the *is a binary or not, and $\brak{ii}$ if it is a binary, then is it commutative or not.
\item Find the particular solution of the differential equation :
\begin{align*}
    \brak{1+e^{2x}}dy+\brak{1+y^2}e^xdx=0.
\end{align*}given that $y\brak{0}=1$.
\item Find the particular solution of differential equation :
\begin{align*}
    x\dfrac{dy}{dx}\sin \dfrac{y}{x}+x-y\sin \dfrac{y}{x}=0
\end{align*},given that$ y\brak{1}=\dfrac{\pi}{2}$.
\item Prove that the relation r in the set $A=\cbrak{1,2,3,4,5,6,7}$ given by $R=\brak{a,b}:\brak{\abs{a-b} }$is even,an equivalence relation.
\item Show that the function f in $A=R-\cbrak{\dfrac{2}{3}}$defined as $f\brak{x}=\dfrac{4x+3}{6x-4}$is one-one and onto.hence,find $f^{-1}$. 
\item Find whether the function f$\brak{x}=\cos\brak{2x+\dfrac{\pi}{4}}$; is increasing or decreasing in the interval $\dfrac{3\pi}{8}<x<\dfrac{5\pi}{8}.$
\item Using vector find the value of $x$ such that that four points $A\brak{x,5,-1},B\brak{3,2,1},c\brak{4,5,5}$ and D$\brak{4,2,-2}$ are co-planar.
\item Prove that :
\begin{align}
 \sin^{-1 }\frac{4}{5}+\tan^{-1}\frac{5}{12}+\cos^{-1}
\frac{63}{65}=\frac{\pi}{2}.   
\end{align}
\item If $ {x^P}{y^Q}=\brak{x+y}^{P+Q}$,prove that
$\dfrac{dy}{dx}+\dfrac{y}{x}$and $\dfrac{d^2y}{dx^2}=0.$
\item Find 
\begin{align}
\int \brak{\sin x.\sin 2x.\sin3x}dx.
\end{align}
\item Differentiate $\tan^{-1}\dfrac{3x-x^3}{1-3x^2},|x|<\dfrac{1}{\sqrt{3}}$ w.r.t.$\tan{-1}\dfrac{x}{\sqrt{1-x^2}}.$
\item If $\sqrt{1-x^2}+\sqrt{1-y^2}=a\brak{x-y},\abs{x}<1,\abs{y}<1,$show that $\dfrac{dy}{dx}=\sqrt{\dfrac{1-y^2}{1-x^2}}.$
\item Using properties of determinants, prove that following:
\begin{align*}
    \mydet{a^2&bc&ac+c^2\\a^2+ab&b^2&ac\\ab&b^2+bc&c^2}=4a^2b^2c^2.
\end{align*}
%\mydet{a^2&bc&ac+c^2\\a^2+ab&b^2&ac\\ab&b^2+bc&c^2}=4a^2b^2c^2.$
\item Evaluate :
\begin{align}
\int_{-1}^{2}|x^2-x|dx.
\end{align}
\item Find the equation of planes passing through the intersection of planes$ \overrightarrow r.\brak{3\hat{i}+6\hat{j}}+12=0$ and$ \overrightarrow r.\brak{3\hat{i}-\hat{j}+4\hat{k}}=0 $and are at a unit distance from origin.
\item Using  integration, find the area of following region :$\cbrak{\brak{x,y}:x^2+y^2\leq16a^2 and y^2\leq6ax}.$
\item Using integration,find the area of $\triangle ABC$ bounded by the lines
\begin{align}
4x-y+5&=0,\\x+y-5&=0 \\ x-4y+5&=0.
\end{align}
\item Find the vector equation of the line passing through $\brak{2,1,-1}$and parallel to the line.
\begin{align} \overrightarrow r=\brak{\hat{i}+\hat{j}+\lambda \brak{2\hat{i}-\hat{j}+\hat{k}}}.\end{align} Also, find the distance between these two lines.
\item Find the coordination of the foot $Q$ of the perpendicular drawn from the point$ P \brak{1,3,4}$to the plane $2x-y+z+3=0$.Find the distance$ PQ$ and the  image of P treating the plane as a mirror.
\item Using elementary row transformation, find the inverse of the matrix \myvec{3&0&-1\\2&3&0\\0&4&1}.
\item Using matrix,solve the following system of linear equations: \begin{align} 2x+3y+10z=4 \\4x-6y+5z=1\\ 6x+9y-20z=2.\end{align}
\item The sum of the perimeters of circle and a square is K is some constant. Prove that the sum of their area is least when the side of the square is twice the radius of the radius of the circle.
\item A bag contains 5 red and 3 black balls and another bag contain 2 red and 6 black balls.Two balls are drawn at random $\brak{without replacement}$ from one of the bags an both are found to be red. Find the probability that balls are drawn from the first bag.
\item If $x,y,z$ are different and $\delta =\myvec{x&x^2&x^3-1\\y&y^2&y^3-1\\z&z^2&z^3-1}=0$, then using properties of determination,show that $xyz=1$.
\item Using vectors, find the value f $x$ such that the four option $ A\brak{x,5,-1},B\brak{3,2,1},C \brak{4,5,5}$ and D $\brak{4,2,-2} $are co-planar.
\item differentiate $ \tan^{-1} \dfrac{3x-x^3}{1-3x^2},\abs{x}<\dfrac{1}{\sqrt{3}} $ w.r.t. $\tan^{-1}\dfrac{x}{\sqrt{1-x^2}}.$
\item If $ y=\brak{\sin x}^x+\sin{-1}\brak{\sqrt{1-x^2}},$ then find $\dfrac{dy}{dx}.$
\item Find
\begin{align}
\int\brak{\cos2x\cos4x\cos6x} dx. 
\end{align}
\item Find the interval in which the function f given by \begin{align}
f\brak{x}=\sin2x+\cos2x, 0\leq x\leq \pi \end{align} is strictly decreasing.
\item A company manufactures two types of novelty souvenirs made of plywood. souvenirs of type A require $5$ minutes each for cutting and $10$ minutes each for assembling.souvenirs of type $B$ require $8$ minutes each for cutting and $8$ minutes each for assembling. there are 3 hours $20$ minutes available for cutting and $4$hours for assembling. the profit for type $A$ souvenirs is \rupee$ 100$ each and for type $B$ souvenirs, profit is \rupee $120$ each. How many souvenirs of each type should the company manufacture in order to maximum the profit ? Formulate the problem as a LPP and then solve it graphically.
\item A card from a pack of $52$  playing cards is lost. from the remaining cards of the pack,two cards are drawn at random $\brak{without}$ and both are found to be spades. Find the probability of the lost card being a spade. 
\item Prove that the radius of the right circular cylinder of greatest curved surface area which can be inscribed in a given cone is half of that of the cone.
\end{enumerate}
\end{document}

